\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliographie}

\bibitem{nextjs}
Vercel Inc.
\textit{Next.js Documentation - The React Framework for Production}.
\url{https://nextjs.org/docs}, 2024.

\bibitem{prisma}
Prisma Data Inc.
\textit{Prisma - Next-generation ORM for Node.js and TypeScript}.
\url{https://www.prisma.io/docs}, 2024.

\bibitem{nextauth}
NextAuth.js Contributors.
\textit{NextAuth.js Documentation - Authentication for Next.js}.
\url{https://next-auth.js.org}, 2024.

\bibitem{react}
Meta Platforms Inc.
\textit{React - A JavaScript Library for Building User Interfaces}.
\url{https://react.dev}, 2024.

\bibitem{typescript}
Microsoft Corporation.
\textit{TypeScript Documentation - JavaScript with Syntax for Types}.
\url{https://www.typescriptlang.org/docs}, 2024.

\bibitem{postgresql}
The PostgreSQL Global Development Group.
\textit{PostgreSQL Documentation - The World's Most Advanced Open Source Relational Database}.
\url{https://www.postgresql.org/docs}, 2024.

\bibitem{tailwind}
Tailwind Labs Inc.
\textit{Tailwind CSS Documentation - Rapidly Build Modern Websites}.
\url{https://tailwindcss.com/docs}, 2024.

\bibitem{zod}
Colinhacks.
\textit{Zod - TypeScript-first Schema Validation}.
\url{https://zod.dev}, 2024.

\bibitem{scrumguide}
Schwaber, Ken and Sutherland, Jeff.
\textit{The Scrum Guide - The Definitive Guide to Scrum: The Rules of the Game}.
Scrum.org, November 2020.

\bibitem{agilemanifesto}
Beck, Kent et al.
\textit{Manifesto for Agile Software Development}.
\url{https://agilemanifesto.org}, 2001.

\bibitem{cleancode}
Martin, Robert C.
\textit{Clean Code: A Handbook of Agile Software Craftsmanship}.
Prentice Hall, 2008.

\bibitem{pragmaticprogrammer}
Hunt, Andrew and Thomas, David.
\textit{The Pragmatic Programmer: From Journeyman to Master}.
Addison-Wesley Professional, 2019. 20th Anniversary Edition.

\bibitem{designpatterns}
Gamma, Erich et al.
\textit{Design Patterns: Elements of Reusable Object-Oriented Software}.
Addison-Wesley Professional, 1994.

\bibitem{nodejs}
OpenJS Foundation.
\textit{Node.js Documentation}.
\url{https://nodejs.org/docs}, 2024.

\bibitem{jwt}
Jones, M., Bradley, J., and Sakimura, N.
\textit{JSON Web Token (JWT) - RFC 7519}.
Internet Engineering Task Force (IETF), May 2015.

\bibitem{owasp}
OWASP Foundation.
\textit{OWASP Top Ten - Web Application Security Risks}.
\url{https://owasp.org/www-project-top-ten}, 2021.

\bibitem{restapi}
Fielding, Roy Thomas.
\textit{Architectural Styles and the Design of Network-based Software Architectures}.
Doctoral dissertation, University of California, Irvine, 2000.

\bibitem{uml}
Object Management Group (OMG).
\textit{Unified Modeling Language (UML) Specification}.
\url{https://www.omg.org/spec/UML}, 2017.

\bibitem{softwareeng}
Sommerville, Ian.
\textit{Software Engineering}, 10th Edition.
Pearson, 2015.

\bibitem{databasesystems}
Elmasri, Ramez and Navathe, Shamkant B.
\textit{Fundamentals of Database Systems}, 7th Edition.
Pearson, 2015.

\bibitem{webdev}
Duckett, Jon.
\textit{JavaScript and jQuery: Interactive Front-End Web Development}.
Wiley, 2014.

\bibitem{react-patterns}
Stoyan, Stefanov.
\textit{React Design Patterns and Best Practices}, 2nd Edition.
Packt Publishing, 2019.

\bibitem{microservices}
Newman, Sam.
\textit{Building Microservices: Designing Fine-Grained Systems}, 2nd Edition.
O'Reilly Media, 2021.

\bibitem{devops}
Kim, Gene et al.
\textit{The DevOps Handbook: How to Create World-Class Agility, Reliability, and Security}.
IT Revolution Press, 2016.

\bibitem{security}
Anderson, Ross.
\textit{Security Engineering: A Guide to Building Dependable Distributed Systems}, 3rd Edition.
Wiley, 2020.

\bibitem{git}
Chacon, Scott and Straub, Ben.
\textit{Pro Git}, 2nd Edition.
Apress, 2014.
\url{https://git-scm.com/book}, Libre accès.

\bibitem{mdn}
Mozilla Developer Network (MDN).
\textit{Web Technology Documentation}.
\url{https://developer.mozilla.org}, 2024.

\bibitem{bcrypt}
Provos, Niels and Mazières, David.
\textit{A Future-Adaptable Password Scheme}.
Proceedings of USENIX Annual Technical Conference, 1999.

\bibitem{acid}
Gray, Jim and Reuter, Andreas.
\textit{Transaction Processing: Concepts and Techniques}.
Morgan Kaufmann, 1992.

\bibitem{banking-security}
Basel Committee on Banking Supervision.
\textit{Principles for the Sound Management of Operational Risk}.
Bank for International Settlements, June 2011.

\bibitem{gdpr}
European Parliament and Council.
\textit{Regulation (EU) 2016/679 - General Data Protection Regulation (GDPR)}.
Official Journal of the European Union, April 2016.

\bibitem{stack-overflow}
Stack Overflow.
\textit{Developer Community and Q\&A Platform}.
\url{https://stackoverflow.com}, 2024.

\bibitem{github}
GitHub Inc.
\textit{GitHub Documentation - Code Hosting and Collaboration Platform}.
\url{https://docs.github.com}, 2024.

\bibitem{vercel}
Vercel Inc.
\textit{Vercel Documentation - Platform for Frontend Frameworks}.
\url{https://vercel.com/docs}, 2024.

\bibitem{rechart}
Recharts Contributors.
\textit{Recharts - Redefined Chart Library Built with React and D3}.
\url{https://recharts.org}, 2024.

\bibitem{zustand}
Poimandres Contributors.
\textit{Zustand - A Small, Fast and Scalable State-Management Solution}.
\url{https://github.com/pmndrs/zustand}, 2024.

\bibitem{radixui}
WorkOS Inc.
\textit{Radix UI - Unstyled, Accessible Components for Building High-Quality Design Systems}.
\url{https://www.radix-ui.com}, 2024.

\bibitem{shadcn}
shadcn.
\textit{shadcn/ui - Beautifully Designed Components Built with Radix UI and Tailwind CSS}.
\url{https://ui.shadcn.com}, 2024.

\bibitem{medium-tech}
Medium.
\textit{Articles et Retours d'Expérience Techniques}.
\url{https://medium.com/tag/programming}, 2024.

\bibitem{css-tricks}
CSS-Tricks.
\textit{Articles on Web Design and Development}.
\url{https://css-tricks.com}, 2024.

\end{thebibliography}

\newpage
